Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2020-10-15 si.tex
Add table for robustness.

>>>>

\section{Robustness experiment}

\begin{table}
\caption{\label{table1}Summary of out-of-sample accuracy for all cross-validation, robustness experiments.
For each fold, one data point in the training set is changed to either 5 times or $\frac{1}{5}$ times its original value.
All test data is kept the same. 
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries. 
Results that are significantly better or worse than the baseline (at the 95\% significance level) are indicated with a dagger.
}
\centering
\fbox{%
\begin{tabular}{*{5}{l}}
{\bf Cross-validation} & {\bf Country}  & {\bf Baseline} & {\bf Prev GP} & {\bf Joint} \\
\hline
Random & Indonesia  &  &   &  \\
& Senegal 13.35 & 13.28 & 14.47  &  \\
& Madagascar  &  & &  \vspace{3mm}\\
Spatial & Indonesia &  &  &  \\
& Senegal 11.70 & 11.53 & 13.97   &  \\
& Madagascar &  &   &  \\
\end{tabular}}
\end{table}
